\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-22 paper/main.tex
minor tweaks to conclusion and contributions

The \texttt{davos} package supports reproducible research by providing
a novel lightweight system for sharing notebook-based code. But
perhaps the most exciting uses of the \texttt{davos} package are those
that we have \textit{not} yet considered or imagined. We hope that the
Python community will find \texttt{davos} to provide a convenient
means of managing project dependencies to facilitate code sharing. We
also hope that some of the more advanced applications of our package
might lead to new insights or discoveries.

@@

\textbf{Paxton C. Fitzpatrick}: Conceptualization, Methodology,
Software, Validation, Writing - Original Draft,
Visualization. \textbf{Jeremy R. Manning}: Conceptualization,
Resources, Validation, Writing - Review \& Editing, Supervision,
Funding acquisition.

>>>>

The \texttt{davos} package supports reproducible research by providing
a novel, lightweight system for sharing notebook-based code. But
perhaps the most exciting uses of the \texttt{davos} package are those
that we have \textit{not} yet considered or imagined. We hope that the
research and scientific Python communities will find \texttt{davos} to provide a convenient
means of managing project dependencies to facilitate code sharing and collaboration. We
also hope that some of the more advanced applications of our package
might lead to new insights or discoveries.

@@

\textbf{Paxton C. Fitzpatrick}: Conceptualization, Methodology,
Software, Validation, Writing - Original Draft,
Visualization. \textbf{Jeremy R. Manning}: Conceptualization,
Resources, Validation, Writing - Review \& Editing, Visualization, Supervision,
Funding acquisition.
